A First Effort for a Distributed Segment-based Approach on Topology-agnostic Self-Assembled Nano Networks

### 2013-09-19 trunk/PAPER/simulation.tex
Fixes

\section{Simulation environment}

@@

\subsection{Nanoxim tool}

In order to quantitatively and qualitatively evaluate the proposed approach a
specific simulation environment has been developed, resulting in
the open source and freely available project called Nanoxim~\cite{}.
Nanoxim is a SystemC tool based on a almost rewritten
version of the Noxim Network-on-Chip simulator~\cite{}. While some
complex features have been removed (e.g. wormhole, congestion/topology
aware routing and selection strategies) new features specifically
taylored for nanoscale scenario were introduced, e.g. the ability to simulate a random
network, the implementation of the DiSR to obtain the segment topology
and the support for defective links and nodes.

%------------------------------------------------------------------------------
\subsection{Experimental setup}
The following parameters have been taken into account when
performing the DiSR simulation:
\begin{itemize}
\item {S}: Size of the network, intended as number of nodes, on a
range from 10x10 to 100x100 sized networks. 
\item {\% defective links}: the probability that each link is
disconnected or not present, from 0 the amount that yelds
no more segments.
\item {\% defective nodes}: the probability that a node is not
working, thus having all its attached links not useful for DiSR setup.
Same range as defective links parameter.
\item {Bootstrap node}: the node used from upper layer (e.g. microscale)
to inject the DiSR process. When not explicitly investigating the
impact of each single bootstrap choice, a set representative regions have been
considered, i.e. the central part of the network and the edge corners
\end{itemize}

@@

Further, to evaluate how DiSR compares against the centralized segment
based algorithm, the following metrics have been adopted:
\begin{itemize}
\item {Average Path Lenght}:
\item {Average Link Weight}:
\item {Unidirectional restrictions:}
\item {Number of Segments}:
\end{itemize}

Since the distribution of defects and thus the resulting topology is randomly
generated, a set of simulations with different seeds has been run
for each system configuration. We found that TODO repetitions are
required in order to obtain statistically significant results.

\subsection{Other optimisations}
Some optimisation parameters, which demostrated to improve the DiSR
results have been fixed to some good values, but are not subject to
further investigation; once again the focus here is not the
optimal set of segments, but just demostrating a working approach. 
These are optimisations are:
\begin{itemize}
\item{cycle\_links}: max number of retries across the set of links of
each node. While searching for a free link due an incoming request,
the same request is cancelled after a given number of tries. This
gives to preceding node change to test a different paths. Default is set to 1.
\item{bootstrap\_timeout}: number of time units that a bootstrap node
should wait before assuming that a livelock in the starting segment
process has occurred. In the worst case, we can imagine that longest
path required is the one returning to the bootstrap node after having
travelled across all the links. So, althought this is just an extreme
situation, a good upper limit can be safely be set to NxN.
\item{bootstrap\_immunity}: in order to avoid the failure of the whole DiSR
setup process, a bootstrap node should not have defective links.
Enabling this optimisation, a bootstrap node is immune to defects.
We may think of a pre-boostrap phase that properly selects (from upper
layer via) a bootstrap node which is tested as properly connected. We
enabled this optimisation, however empirical tests showed us that only
simulations using bootstrap nodes placed on edges would be heavily
affected, since these are nodes starting with a lower number of links,
e.g. corner nodes could only have two connected direction, so even a
defective link could prevent starting segment packet to return to
bootstrap to close the loop a create the segment.

\end{itemize}

>>>>

\section{Simulation and Results}

@@

\subsection{Nanoxim environment}

In order to quantitatively and qualitatively evaluate the proposed approach a
specific simulation environment has been developed, resulting in
the open source and freely available project called
Nanoxim~\cite{nanoxim}.
Nanoxim is a SystemC tool based on a almost rewritten
version of the Noxim Network-on-Chip simulator~\cite{noxim}. While some
complex features have been removed (e.g. wormhole, congestion/topology
aware routing and selection strategies) new features specifically
taylored for nanoscale scenario were introduced, e.g. the ability to simulate a random
network, the implementation of the DiSR to obtain the segment topology
and the support for defective links and nodes.

%------------------------------------------------------------------------------
\subsection{Experimental setup}
The following parameters have been taken into account when
performing the DiSR simulation:
\begin{itemize}
\item {\emph{Size of the network}}: number of nodes, on a
range from 10x10 to 100x100 sized networks. 
%\item {\% defective links}: the probability that each link is
%disconnected or not present, from 0 the amount that yelds
%no more segments.
\item {\emph{\% defective nodes}}: the probability that a node is not
working, thus having all its links cannot be utilized during DiSR setup.  
%Same range as defective links parameter.
\item {Bootstrap node}: the node used from upper layer 
to inject the DiSR process. When not explicitly investigating the
impact of each single bootstrap choice, a set representative regions have been
considered, i.e. the central part of the network and the edge corners
\end{itemize}

@@

Further, to evaluate how DiSR compares against the centralized segment
based algorithm, the following metrics have been adopted:
\begin{itemize}
%\item {Average Path Lenght}:
%\item {Average Link Weight}:
\item {Unidirectional restrictions:}
\item {Number of Segments}:
\end{itemize}

Since the distribution of defects and thus the resulting topology is randomly
generated, a set of simulations with different seeds has been run
for each system configuration. We found that 20 repetitions are
required in order to obtain statistically significant results.

% TODO: long paper
%\subsection{Other optimisations}
%Some optimisation parameters, which demostrated to improve the DiSR
%results have been fixed to some good values, but are not subject to
%further investigation; once again the focus here is not the
%optimal set of segments, but just demostrating a working approach. 
%These are optimisations are:
%\begin{itemize}
%\item{cycle\_links}: max number of retries across the set of links of
%each node. While searching for a free link due an incoming request,
%the same request is cancelled after a given number of tries. This
%gives to preceding node change to test a different paths. Default is set to 1.
%\item{bootstrap\_timeout}: number of time units that a bootstrap node
%should wait before assuming that a livelock in the starting segment
%process has occurred. In the worst case, we can imagine that longest
%path required is the one returning to the bootstrap node after having
%travelled across all the links. So, althought this is just an extreme
%situation, a good upper limit can be safely be set to NxN.
%\item{bootstrap\_immunity}: in order to avoid the failure of the whole DiSR
%setup process, a bootstrap node should not have defective links.
%Enabling this optimisation, a bootstrap node is immune to defects.
%We may think of a pre-boostrap phase that properly selects (from upper
%layer via) a bootstrap node which is tested as properly connected. We
%enabled this optimisation, however empirical tests showed us that only
%simulations using bootstrap nodes placed on edges would be heavily
%affected, since these are nodes starting with a lower number of links,
%e.g. corner nodes could only have two connected direction, so even a
%defective link could prevent starting segment packet to return to
%bootstrap to close the loop a create the segment.
%\end{itemize}
